Network Configuration Synthesis with Abstract Topologies \vspace{1cm}

### 2017-03-07 paper/abstraction/paper.tex
adding to section 7

@@

The translation from the PG to per-device templates that run the distributed BGP protocol involves several ideas.

\para{Route filtering}

>>>>

\vspace{2em}
\begin{figure*}[t!]\small%

  \hrulefill%

  \vspace{1em}%
  \begin{minipage}[t]{.47\linewidth}
  \hdr{ABGP Syntax}{}
  \vspace*{-1\baselineskip}
  %
  \[ \begin{array}{rclr}
     d    &   & & \textit{integer} \\
     c    &   & & \textit{community} \\
     l    &   & & \textit{location} \\
     t    &::=& \$x \BNFALT d.d.d.d/[d..d] & \textit{predicate} \\
     ns   &::=& \{ l_1, ~\dots,~ l_k \} & \textit{peers} \\
     ma   &::=& d : ({ns}_1, c_1) \rightarrow ({ns}_2, c_2) & \textit{match action} \\
     pc   &::=& ma_1, \dots, ma_k & \textit{prefix config} \\
     rc   &::=& t_1 \rightarrow {pc}_1, ~\dots,~ t_k \rightarrow {pc}_k & \textit{router config} \\
     abgp &::=& l_1 \rightarrow {rc}_1, ~\dots,~ l_k \rightarrow {rc}_k & \textit{abgp policy} \\%
  \end{array} \]%%

  \end{minipage}
  %
  %
  \begin{minipage}[t]{.49\linewidth}
  \hdr{Compilation}{}
  \vspace*{-1\baselineskip}
  %
  \[ \begin{array}{l}
     \mathrm{compile}_\mathrm{ABGP}( (t_1,PG_1,ord_1), \dots, (t_k,PG_k,ord_k), G ) = \\
     ~~~~~ [~ l \rightarrow rc ~\vert~ l \in \mathrm{internal}(G.V), ~rc = \mathrm{append}_i~  \\
     ~~~~~~~~~~~~~~~ [~ t_i \rightarrow [~ ma ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~~~~ m \leftarrow (l,q_m) \in PG_i, \\
     ~~~~~~~~~~~~~~~~~~~~~ pin \leftarrow \mathrm{adjIn}(PG_i,m), \\
     ~~~~~~~~~~~~~~~~~~~~~ (in,q_n) \leftarrow \{ (bs,q_n) ~\vert~ bs=\{b ~\vert~ (b,q_n) \in pin \}, bs \neq \emptyset \}, \\
     ~~~~~~~~~~~~~~~~~~~~~ out \leftarrow \{ c ~\vert~ (c,\_) \in \mathrm{adjOut}(PG_i,m) \}, \\
     ~~~~~~~~~~~~~~~~~~~~~ ma = \mathrm{ord}_i(m) : (in,q_n) \rightarrow (out,q_m) ~] ~] ~] \\
     \\
     \mathrm{compile}( p_1, \dots, p_k, G) = \\
     ~~~~~~ \mathrm{compile}_\mathrm{ABGP}(\mathrm{compile}_\mathrm{PG}(p_1,G), \dots, \mathrm{compile}_\mathrm{PG}(p_k,G), G) \\
  \end{array} \]%
  \end{minipage}%

  \vspace{1em}
  \hrulefill%
  %\vspace{1em}%

  \caption{Abstract BGP syntax (left), and compilation from product graphs (right).}
  \label{fig:concretization}
\end{figure*}%

@@

At a high level, the translation from the PG to per-device templates that run the distributed BGP protocol involves the following high-level ideas: First, BGP messages are tagged to record the state of the product graph as messages are passed between routers. This information allows routers to drop messages that do not correspond to any path not permitted. Next, we must search for a ranking of messages for each router in the network such that, under those preferences, the network as a whole satisfies the \sysname policy's preferences. Finally, templates can be soundly concretized for the actual network by replacing instances of abstract neighbors with the union of all concrete neighbors. Finally, by modifying compilation slightly we can further ensure that every configuration depends only on its immediate neighbors. This guarantees that any change made to the concrete topology will result in a minimal number of changes.

We look at each of these steps in turn.

\para{Tagging and Filtering}
